---
title: "W_UP_01"
author: "Monserrat Mendez"
date: "spring 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!--> 

### Plot boxplots

```{r}
boxplot(pushups~position,data=mydata)
```
  
the top of the box above 'line player' represents the 70% percentile of how many pushup the line player did, while the bottom line of the box represents a 22% percentile of the pushups a line payer did. the line payers are doing less pushup then the skill payers.
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
  
this shows that Q1 for the line players is 10.25 and Q1 for skill players with a 31.25.  the median shows the the line payer could do 14 and a half pushups, while the skill player can do 47 and a half pushups. this lets us go to the conclusion that skill players do much more pushups them line players.
  

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
  
this shows is what it would be if there were no differences inbetween the amount of pushups line and skill players are able to do. since the 'P' vaule is vey small the number, we can conclude the number would be insignificant.
  
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
first I opened the boxplot graph to display numerical date explained by in categorical data in which there is two category in which it allowed us to see that: the line payers are doing less pushup then the skill payers. the skill players having 70% at their highest and 25% at their lowest, while the line players are only at 28% in their highest and 10% at their lowest.  
  
  secondly, I oped a Numerical Descriptive Results to show that in Q1 for the line players is 10.25 and Q1 for skill players with a 31.25. along with the other numbers show us the fact the the Skill players do much more pushups then the line players.  
    
  and lastly we run a statistical test also known as a 'T' test, this is when comparing numerical data explained by categorical data when there are only 2 categories. this shows how the changes between the line and skill players would be if there were no differences in between the amount of pushups. which showed that the value of pushsups 'P' was a small therefor the results are insignificant.  

